Refinements for open automata

### 2022-06-16 2021-Refinement/paper/refinementarticle.tex
note?

In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):

>>>>

In both cases note that $g_{13} \implies g_1$\TODO{equal?}, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
